---
title: "Anyl510_Movie_Analysis"
author: "Musarath"
date: "July 2, 2018"
output: html_document
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(magrittr)
require(gsubfn)
require(proto)
require(RSQLite)


library(sqldf)
library(ggplot2)
library(ggpubr)
library(corrplot)
library(tidyverse)

library(readr)
library(tidyr)
library(dplyr)
library(stringr)
library(sqldf)
library(shiny)
library(tcltk)
library(utils)
library(MASS)
```

## Downloading and data clean up - MUSARATH.
## ....tidy data is downloaded into movie.primary.data.csv
```{r echo = FALSE,eval=FALSE}
print("cleanup")
# load movie data file
movies.data = read.csv("movies2.csv",header = TRUE)
#check if the data is loaded properly
dim(movies.data)
# check for any empty or "NA" fields
sum(is.na(movies.data))
# Check for proper data types
str(movies.data)
# appropriate data type conversions
movies.data$Title = as.character(movies.data$Title)
movies.data$Genres = as.character(movies.data$Genres)
#movies.data$Year = as.Date(movies.data$Year)

# data clean up

for (i in 1:nrow(movies.data))
{
  if(str_detect(movies.data$Title[i],";"))
  {
    pos = regexpr(pattern = ';',movies.data$Title[i])
    titlebeg = substring(movies.data$Title[i],pos+1,nchar(movies.data$Title[i]))
    titleend = substring(movies.data$Title[i],1,pos-1)
    movies.data$Title[i] = paste(titlebeg,titleend,sep = '')
  }
}  

#write.csv(movies.data,"E:/HBU/Course_Project/Any_510/ml-1m/test.csv",row.names = FALSE)
# add column for each genre

movies.data = movies.data %>% mutate(Action = 0,Adventure = 0,Animation = 0,Childrens = 0,Comedy = 0,Crime = 0,Documentary =0,Drama=0,Fantasy = 0,Film.Noir=0,Horror=0,Musical=0,Mystery=0,Romance=0,Sci.Fi=0,Thriller=0,War=0,Western=0)

for(i in 1:nrow(movies.data))
{
  movies.data$Action[i] = ifelse(str_detect(movies.data$Genres[i],"Action"),1,0)
  movies.data$Adventure[i] = ifelse(str_detect(movies.data$Genres[i],"Adventure"),1,0)
  movies.data$Animation[i] = ifelse(str_detect(movies.data$Genres[i],"Animation"),1,0)
  movies.data$Childrens[i] = ifelse(str_detect(movies.data$Genres[i],"Childrens"),1,0)
  movies.data$Comedy[i] = ifelse(str_detect(movies.data$Genres[i],"Comedy"),1,0)
  
  movies.data$Crime[i] = ifelse(str_detect(movies.data$Genres[i],"Crime"),1,0)
  movies.data$Documentary[i] = ifelse(str_detect(movies.data$Genres[i],"Documentary"),1,0)
  movies.data$Drama[i] = ifelse(str_detect(movies.data$Genres[i],"Drama"),1,0)
  movies.data$Fantasy[i] = ifelse(str_detect(movies.data$Genres[i],"Fantasy"),1,0)
  movies.data$Film.Noir[i] = ifelse(str_detect(movies.data$Genres[i],"Film.Noir"),1,0)
  
  movies.data$Horror[i] = ifelse(str_detect(movies.data$Genres[i],"Horror"),1,0)
  movies.data$Musical[i] = ifelse(str_detect(movies.data$Genres[i],"Musical"),1,0)
  movies.data$Mystery[i] = ifelse(str_detect(movies.data$Genres[i],"Mystery"),1,0)
  movies.data$Romance[i] = ifelse(str_detect(movies.data$Genres[i],"Romance"),1,0)
  movies.data$Sci.Fi[i] = ifelse(str_detect(movies.data$Genres[i],"Sci.Fi"),1,0)
  
  movies.data$Thriller[i] = ifelse(str_detect(movies.data$Genres[i],"Thriller"),1,0)
  movies.data$War[i] = ifelse(str_detect(movies.data$Genres[i],"War"),1,0)
  movies.data$Western[i] = ifelse(str_detect(movies.data$Genres[i],"Western"),1,0)
  
}
#remove the Genres column
movies.data = movies.data[,-4]


# load user data file
users.data = read.csv("users.csv",header = TRUE)

#load rating data file
rating.data = read.csv("ratings.csv",header = TRUE)

# join the movie and rating tables

data = movies.data %>% left_join(rating.data,by = "MovieId" )
dim(data)

#check for blank fields
any(is.na(data))
sum(is.na(data))
# exclude the NA records
data = na.omit(data)

# join the data (movie and rating combined) with user table
data1 = data %>% left_join(users.data,by = "UserId")

# check for blank records
sum(is.na(data1))

#Rearrange the column names
data1 = data1 %>% select(MovieId:UserId,Gender:Zipcode,TimeStamp,Rating)

data1 =  sqldf("select * from data1 where Zipcode between 15000 and 19700")

# converting age column as factors

for(i in 1:nrow(data1))
{
  if(data1$Age[i] >= 1 & data1$Age[i] <= 18)
  data1$Age[i] = 1
  else
    if(data1$Age[i] >= 19 & data1$Age[i] <='25')
    data1$Age[i] = 2
    else
      if(data1$Age[i] >= 26 & data1$Age[i] <=35)
      data1$Age[i] = 3
      else
        if(data1$Age[i] >= '36' & data1$Age[i] <=50)
        data1$Age[i] = 4
        else 
          if(data1$Age[i] >= 50)
          data1$Age[i] = 5
          
          print(i)
} 

# write to movie.data file
write.csv(data1,"E:/HBU/Course_Project/Any_510/Rahamathullah_Musarath_TeamProject_Proposal/movie.primary.data.csv",row.names = FALSE)

```




## Correlation analysis - MANISHA
## -----------------------------------------------#
# Chi square test for primary dataset
# ***H0: The The two variables are independent***
# ***H1: The The two variables are dependent***
## -----------------------------------------------#

```{r echo=FALSE,warning=FALSE}
myprimarydata <- read.csv("./movie.primary.data.csv")

dim(myprimarydata)



chi1 <- chisq.test(myprimarydata$Action,myprimarydata$Rating, correct = FALSE)
chi1

chi2 <- chisq.test(myprimarydata$Adventure,myprimarydata$Rating, correct = FALSE)
chi2

chi3 <- chisq.test(myprimarydata$Animation,myprimarydata$Rating, correct = FALSE)
chi3

chi4 <- chisq.test(myprimarydata$Comedy,myprimarydata$Rating, correct = FALSE)
chi4

chi5 <- chisq.test(myprimarydata$Crime,myprimarydata$Rating, correct = FALSE)
chi5

chi6 <- chisq.test(myprimarydata$Documentary,myprimarydata$Rating, correct = FALSE)
chi6

chi7 <- chisq.test(myprimarydata$Drama,myprimarydata$Rating, correct = FALSE)
chi7

chi8 <- chisq.test(myprimarydata$Fantasy ,myprimarydata$Rating, correct = FALSE)
chi8

chi9 <- chisq.test(myprimarydata$Film.Noir,myprimarydata$Rating, correct = FALSE)
chi9

chi10 <- chisq.test(myprimarydata$Horror,myprimarydata$Rating, correct = FALSE)
chi10

chi11 <- chisq.test(myprimarydata$Horror,myprimarydata$Rating, correct = FALSE)
chi11

chi12 <- chisq.test(myprimarydata$Musical,myprimarydata$Rating, correct = FALSE)
chi12

chi14 <- chisq.test(myprimarydata$Romance,myprimarydata$Rating, correct = FALSE)
chi14

chi15 <- chisq.test(myprimarydata$Sci.Fi,myprimarydata$Rating, correct = FALSE)
chi15

chi16 <- chisq.test(myprimarydata$Thriller,myprimarydata$Rating, correct = FALSE)
chi16

chi17 <- chisq.test(myprimarydata$War,myprimarydata$Rating, correct = FALSE)
chi17

chi19 <- chisq.test(myprimarydata$Occupation,myprimarydata$Rating, correct = FALSE)
chi19

chi20 <- chisq.test(myprimarydata$Age,myprimarydata$Rating, correct = FALSE)
chi20

chi21<- chisq.test(myprimarydata$Gender,myprimarydata$Rating, correct = FALSE)
chi21

chi13 <- chisq.test(myprimarydata$Mystery,myprimarydata$Rating, correct = FALSE)
chi13

chi16 <- chisq.test(myprimarydata$Thriller,myprimarydata$Rating, correct = FALSE)
chi16

chi18 <- chisq.test(myprimarydata$Western,myprimarydata$Rating, correct = FALSE)
chi18


print("Movie rating is significantly dependent on gender, age, occupation and all genres except mystery, thriller and western")

#' 
#' ##Plotting association
#' 
## ------------------------------------------------------------------------
p1 <-ggplot(myprimarydata,aes(myprimarydata$Gender, myprimarydata$Rating)) + geom_point(aes(color=myprimarydata$Rating ))

p1 + geom_smooth()

p2 <-ggplot(myprimarydata,aes(myprimarydata$Gender, fill = myprimarydata$Rating)) + geom_bar()

p2
p3 <-ggplot(myprimarydata,aes(myprimarydata$Gender, fill = myprimarydata$Rating)) + geom_bar()



```

# ------------------------------------------------#
# ## Chi square test for Secondary dataset 
# ***H0: The The two variables are independent***
# ***H1: The The two variables are dependent***
## ------------------------------------------------#
```{r echo=FALSE,warning=FALSE}

print("....work in progress")


```


#

## Linear regression analysis - NAVYA
```{r echo=FALSE,warning=FALSE}
myprimarydata <- read.csv("./movie.primary.data.csv") 
#View(myprimarydata)

#str(myprimarydata)

myprimarydata$Gender <- as.factor(myprimarydata$Gender)
myprimarydata$Age <- as.factor(myprimarydata$Age)
myprimarydata$Occupation <- as.factor(myprimarydata$Occupation)

indx = sample(1:nrow(myprimarydata),as.integer(0.8*nrow(myprimarydata)))
train = myprimarydata[indx,]
test = myprimarydata[-indx,]

lm = lm(Rating ~ Action + Adventure + Animation +	Childrens +	Comedy +	Crime	+ Documentary + 	Drama	+ Fantasy	+ Film.Noir	+ Horror +	Musical + Mystery	+ Romance	+ Sci.Fi + Thriller +  	War +	Western + Gender + Age + Occupation, data = train)
#summary(lm.fit)

lm.fit = stepAIC(lm,direction = "both")

lm.predict = predict(lm.fit,test)

lm.predict = ceiling(lm.predict)
actual_predicted = data.frame(Actual = test$Rating,Predicted = lm.predict)

cor(actual_predicted)


# We attempted to predict the rating of a movie, based on various factors, such as the Genre of the movie, and the respondent's age group and gender. The initial results were as follows:
primarylinearmodel <- lm(Rating ~ Action + Adventure + Animation +	Childrens +	Comedy +	Crime	+ Documentary + 	Drama	+ Fantasy	+ Film.Noir	+ Horror +	Musical + Mystery	+ Romance	+ Sci.Fi + Thriller +  	War +	Western + Gender + Age, data = myprimarydata)
summary(primarylinearmodel)

print("From the above summary, we can see that there a number of variables with high p-values. Hence we attempted to rerun the model by eliminating such variables.") 

primarylinearmodel_adjusted <- lm(Rating ~ Action + Adventure+ Animation +	Childrens +	Crime	+ Documentary + Drama	+ Fantasy+Film.Noir	+ Horror +	Musical + Mystery	+ Romance	+Sci.Fi +Thriller + 	War +	Western , data = myprimarydata)
summary(primarylinearmodel_adjusted)

par(mfrow = c(2,2))
plot(primarylinearmodel_adjusted)

```

## ANOVA for Primary Dataset - APARNA
```{r echo=FALSE,warning=FALSE}
myprimarydata = read.csv("movie.primary.data.csv")
#anova
myData1.fix.aov <- aov(Rating ~ Age, data=myprimarydata)
anova(myData1.fix.aov)
boxplot(Age ~ Rating,
        data = myprimarydata,
        xlab = "Age",
        ylab = "Rating")

myData2.fix.aov <- aov(Rating ~ Occupation, data=myprimarydata)
anova(myData2.fix.aov)
boxplot(Rating ~ Occupation,
        data = myprimarydata,
        xlab = "Occupation",
        ylab = "Rating")

X = as.factor(myprimarydata$Gender)
myData3.fix.aov <- aov(Rating ~ Gender, data=myprimarydata)
anova(myData3.fix.aov)
boxplot(Rating ~ Gender,
        data = myprimarydata,
        xlab = "Gender",
        ylab = "Rating")


```

## ANOVA for Secondary Dataset - JHANVI
```{r echo = FALSE,warning=FALSE}
mysecondarydata <- read.csv("./Secondary_dataset.csv")

aov(mysecondarydata$Content.Likability.Rating ~ mysecondarydata$Age)
boxplot(mysecondarydata$Content.Likability.Rating ~ mysecondarydata$Age)

aov(mysecondarydata$Content.Likability.Rating ~ mysecondarydata$Gender)
boxplot(mysecondarydata$Content.Likability.Rating ~ mysecondarydata$Gender)

aov(mysecondarydata$Content.Likability.Rating ~ mysecondarydata$Netflix.Future)
boxplot(mysecondarydata$Content.Likability.Rating ~ mysecondarydata$Netflix.Future)

```


